A Review of Neutron Imaging

### 2020-10-13 neutron-imaging/neutron.tex
WIP 13Oct2020

\section{Larmor precession based imaging}\label{s11}
\section{Polarization based imaging}\label{s12}
\section{Imaging of biologically important structures}\label{s13}
\section{Conclusion}\label{s14}
\bibliography{neutron}
\bibliographystyle{plain}
\end{document}

>>>>

\section{Larmor precession based imaging}\label{s11}
A magnetic dipole of moment $\vec{\mu}$ experiences a torque $\vec{\tau} = 
\vec{\mu} \times \vec{B}$ in a magnetic field $\vec{B}$. If $\gamma$ is the
gyromagnetic ratio of the dipole then $\vec{\mu} = \gamma\vec{L}$, $\vec{L}$
being its angular momentum. Since
\begin{equation}\label{s11e1}
\frac{d\vec{L}}{dt} = \vec{\tau} = \gamma\vec{L} \times \vec{B},
\end{equation}
when $\vec{B}$ is not parallel (or anti-parallel) to $\vec{L}$, the vector 
$\vec{L}$ precesses about $\vec{B}$ with a frequency $\omega = \gamma B$, 
called the Larmor frequency. When a polarized beam of neutrons is made to
pass through a magnetic material, the spin vector of the neutrons undergoes
Larmor precession in the internal magnetic field of material. The angle of 
spin changes by an amount that depends on the magnitude of the magnetic field
and the time the neutron was present in it. The change in the spin orientation
can be measured by a spin analyzer. Different regions of the material show
different changes in spin orientation. By mapping the change in spin to grey
scale one can create a contrast between these regions 
\cite{kardjilov2011neutron}. This is the principle behind Larmor precession
based neutron imaging. If the magnetic fields are sufficiently low so that
the Larmor tilt is never more than $\pm\pi$, quantitative 2-d and 3-d imaging
is possible. It was used to study the trapping of magnetic flux in type-I 
superconductors \cite{kardjilov2008three}. This idea can be extended to 
examine the how a ferromagnet becomes a paramagnet past the Curie temperature.
When a beam of polarized neutrons falls on a ferromagnet, the randomly oriented
magnetic domains of the ferromagnet depolarize the beam. When the same material
is heated, the domains begin to weaken and beyond the Curie temperature they
disappear altogether. The polarized beam is not transmitted undisturbed. This
technique can be used to study the change in magnetic properties of materials
in response to changing stress, pressure or applied electromagnetic fields
\cite{kardjilov2011neutron}.

\section{Polarization based imaging}\label{s12}
\section{Imaging of biologically important structures}\label{s13}
\section{Conclusion}\label{s14}
\bibliography{neutron}
\bibliographystyle{plain}
\end{document}
